### 2021-02-11 yfcc100m/paper/vldb2021/design.tex
Update figures, other minor fixes

VDMS and its components are fully available as open source projects
% \footnote{https://github.com/IntelLabs/\{vdms, pmgd\}}.
\footnote{https://github.com/\{Not shown during submission\}}.
We briefly describe each of the main components as follows:

@@

Listing~\ref{findimagegeo} shows a sample query. 
In this particular example, the transaction retrieves 
all the images of \textit{alligators} 
with probability higher than 0.66,
filter by latitude and longitude within 1 degree, 
apply a resize operation to make the images 224x224, 
rotate the images 45.34 degrees, 
and return the images as "png" files. 
It is important to note how the API natively supports basic building 
blocks of visual data processing, like resize, rotation, or transcoding
(changing output formats and encodings).
The API allows interaction with metadata, images, videos, 
and feature vectors in a similar fashion, and it is fully 
documented on the project's Github 
wiki~\footnote{https://github.com/\{Not shown during submission\}}.
% wiki~\footnote{https://github.com/IntelLabs/vdms/wiki/API-Description}.

>>>>

VDMS and its components are fully available as open source projects
\footnote{https://github.com/IntelLabs/\{vdms, pmgd\}}.
We briefly describe each of the main components as follows:

@@

Listing~\ref{findimagegeo} shows a sample query.
In this particular example, the transaction retrieves
all the images of \textit{alligators}
with probability higher than 0.66,
filter by latitude and longitude within 1 degree,
apply a resize operation to make the images 224x224,
rotate the images 45.34 degrees,
and return the images as "png" files.
It is important to note how the API natively supports basic building
blocks of visual data processing, like resize, rotation, or transcoding
(changing output formats and encodings).
The API allows interaction with metadata, images, videos,
and feature vectors in a similar fashion, and it is fully
documented on the project's Github
wiki~\footnote{https://github.com/IntelLabs/vdms/wiki/API-Description}.

### 2021-02-11 yfcc100m/paper/vldb2021/eval.tex
Update figures, other minor fixes

It is important to note that when querying for images with certain
\textit{autotags}, we also apply a filter using the probability.
For instance, we only retrieve images with an autotag \textit{alligator}
and a probability higher than 92\%.
These probabilities are both present in VDMS (in the form of a property
of the \textit{connection} between the image and that \textit{autotag}),
as well as in MySQL (in the form of a column in the \textit{autotags} table
that links images with tags).
In the case of VDMS, the query involves a graph traversal query that starts
from the \textit{autotag} node and ends in the images node,
following \textit{connections} between the image and that \textit{autotag}).
In the case of the baseline implementation,
the query involves JOIN operations between the 3 tables.
The implementation of this evaluation, as well as all the queries, are available
under the benchmarks branch of the VDMS project
\footnote{https://github.com/\{Not shown during submission\}}
% \footnote{https://github.com/IntelLabs/vdms/ under benchmark/benckmarks/visual\_storm/yfcc100m},
and some examples of the queries can be found in the appendix of this
paper.

\begin{figure}[ht]
\includegraphics[width=\columnwidth]{figures/concurrency_comparison}
\caption{Concurrency Analysis on \textit{q2} (\textit{1tag\_resize}).
Hardware concurrency (number of physical cores in each system)
is shown with a blue vertical line (hw-concurrency = 56).
Top figure shows aggregated throughput (transactions per second)
when retrieving only metadata associated with the images, as the number of
concurrent clients increase.
Bottom figure shows aggregated throughput (images per second) when retrieving
resized versions of the images, as the number of concurrent clients increases.}
\label{fig:concurrency_comparison}
\end{figure}

@@

\begin{figure*}[ht!]
\begin{subfigure}{.5\linewidth}
  \centering
  % include first image
  \includegraphics[width=\columnwidth]{figures/queries_throughput_56_q1_q2_q3}
  \caption{\textit{q1}(red), \textit{q2}(blue),and \textit{q3}(orange).}
  \label{fig:q1_q2}
\end{subfigure}
\begin{subfigure}{.5\linewidth}
  \centering
  % include second image
  \includegraphics[width=\columnwidth]{figures/queries_throughput_56_q4_q5}
  \caption{\textit{q4}(black), and \textit{q5}(pink).}
  \label{fig:q3_q4}
\end{subfigure}
\caption{Performance Analysis using 5 queries from our use-case
described in the Experimental Setup Section.
We show queries in different figures for readability reasons.
Top figures show the throughput of the queries for
just retrieving metadata associated with the images.
Bottom figures show the throughput when retrieving both metadata and images,
plus operations applied to images when applicable (queries 2, 3, 4 and 5).
The experiments show the performance of both systems (VDMS and baseline) as the
database size increases.
These queries were run using 56 simultaneous clients (nthr = 56),
and averaged out of 10 runs (niter = 10),
each client running 2 transactions (ntags = 2).}
\label{fig:q_throughput_56}
\end{figure*}

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width=\textwidth]{figures/summary_images}
\caption{Summary of performance gains for all queries.
We see up to 35x speedup (\textit{q2}), and an average of about 15x.
More importantly, we see that the speedup grow as the database size increases,
showing that VDMS scales better than the baseline.}
\label{fig:summary_images}
\end{figure*}

>>>>

It is important to note that when querying for images with certain
\textit{autotags}, we also apply a filter using the probability.
For instance, we only retrieve images with an autotag \textit{alligator}
and a probability higher than 92\%.
These probabilities are both present in VDMS (in the form of a property
of the \textit{connection} between the image and that \textit{autotag}),
as well as in MySQL (in the form of a column in the \textit{autotags} table
that links images with tags).
In the case of VDMS, the query involves a graph traversal query that starts
from the \textit{autotag} node and ends in the images node,
following \textit{connections} between the image and that \textit{autotag}).
In the case of the baseline implementation,
the query involves JOIN operations between the 3 tables.
The implementation of this evaluation, as well as all the queries, are available
under the benchmarks branch of the VDMS project
\footnote{https://github.com/IntelLabs/vdms/ under benchmark/benckmarks/visual\_storm/yfcc100m},
and some examples of the queries can be found in the appendix of this
paper.

\begin{figure*}[ht]
\includegraphics[width=\textwidth]{figures/plot_conc_1tag_loc20_resize_mosaic_results_throughput_db_size}
\caption{Concurrency Analysis on \textit{q3} (\textit{1tag\_resize\_geo}).
Hardware concurrency (number of physical cores in each system)
is shown with a blue vertical line (hw-concurrency = 56).
Top figure shows aggregated throughput (transactions per second)
when retrieving only metadata associated with the images, as the number of
concurrent clients increase.
Bottom figure shows aggregated throughput (images per second) when retrieving
resized versions of the images, as the number of concurrent clients increases.}
\label{fig:concurrency_comparison}
\end{figure*}

\begin{figure*}[ht]
\includegraphics[width=\textwidth]{figures/plot_conc_10M_mosaic_results_throughput}
\caption{Concurrency Analysis for all the queries on the 10M database).
Hardware concurrency (number of physical cores in each system)
is shown with a blue vertical line (hw-concurrency = 56).
Top figure shows aggregated throughput (transactions per second)
when retrieving only metadata associated with the images, as the number of
concurrent clients increase.
Bottom figure shows aggregated throughput (images per second) when retrieving
resized versions of the images, as the number of concurrent clients increases.}
\label{fig:concurrency_comparison_10M}
\end{figure*}

@@

\begin{figure*}[ht]
\includegraphics[width=\textwidth]{figures/plot_56_mosaic_query_times}
\caption{Performance Analysis using all queries from our use-case
described in the Experimental Setup Section.
We show queries in different figures for readability reasons.
Top figures show the throughput of the queries for
just retrieving metadata associated with the images.
Bottom figures show the throughput when retrieving both metadata and images,
plus operations applied to images when applicable (queries 2, 3, 4 and 5).
The experiments show the performance of both systems (VDMS and baseline) as the
database size increases.
These queries were run using 56 simultaneous clients (nthr = 56),
and averaged out of 10 runs.}
\label{fig:q_performance_56}
\end{figure*}

\begin{figure*}[ht]
\includegraphics[width=\textwidth]{figures/plot_56_mosaic_results_throughput}
\caption{Throughput Analysis using all queries from our use-case
described in the Experimental Setup Section.
We show queries in different figures for readability reasons.
Top figures show the throughput of the queries for
just retrieving metadata associated with the images.
Bottom figures show the throughput when retrieving both metadata and images,
plus operations applied to images when applicable (queries 2, 3, 4 and 5).
The experiments show the performance of both systems (VDMS and baseline) as the
database size increases.
These queries were run using 56 simultaneous clients (nthr = 56),
and averaged out of 10 runs.}
\label{fig:q_throughput_56}
\end{figure*}

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width=\textwidth]{figures/plot_56_query_times_speedup}
\caption{Summary of performance gains for all queries.
We see up to 35x speedup (\textit{q2}), and an average of about 15x.
More importantly, we see that the speedup grow as the database size increases,
showing that VDMS scales better than the baseline.}
\label{fig:summary_images}
\end{figure*}
